\documentclass[../documentation.tex]{subfiles}

\begin{document}

\subsection{mandate}

The \texttt{mandate} folder contains all the documents regarding
the project (documentation and diary).

\subsection{worker}

\texttt{worker/} is the Rust project for the backend service.
The worker consumes messages from the AMQP server
and processes them by interacting with the database.

\subsection{webapp}

\texttt{webapp/} contais the softwre regarding the webserver and frontend.

\subsubsection{webserver}

\textit{webserver} is the Rust project for the webserver.
This program serves the web page and handles
the API routes. It send messages to the AMQP server
and awaits the responses once the requests are processed
by a backend server.

\subsubsection{frontend}

\textit{frontend} is the program containing Rust code which is compiled to WebAssembly.
This project be compield to a WASM module and interacted with with JavaScript on the frontend.

\subsection{common}

\texttt{common/} is a collection of own Rust libraries
shared accross the programs.

\subsubsection{config}

\textit{common} is a library to help parse the TOML configuration files.
This library is used by the webserver and worker programs.

\subsubsection{database}

\textit{database} is a library wrapper around the database structure
of this project. It is only used by the worker server.

\subsubsection{messaging}

\textit{messaging} is a library to
publish and consume messages to an AMQP server.
The request/reply pattern is also available.
This library is used both by the websever
and worker.

\end{document}