\documentclass[../documentation.tex]{subfiles}

\begin{document}

\subsection{WebAssembly}

WebAssembly (wasm) is a portable low-level language supported by all majors browsers.
It can be used for a variety of things within the browser and can be mixed
with HTML and JavaScript.
WebAssembly does not need to be parsed by the browser since it is already
in a binary format. \\
% cite variety of things with https://webassembly.org/docs/use-cases/
At the time fo writing, WebAssembly is not widely used
and it is not always faster than JavaScript based applications.
However, is it my opinion and hope that it will
better in the future and that it will become a standard in
web development.

\subsection{Rust}

Rust is a generic compiled programming language.
The code is compiled using LLVM to machine code and its speed
is comparable to C and C++.
Rust is the first programming language to guarantee memory safety;
memory is not manually freed nor garbage collected.
It is not possible to dereference a null pointer, cause memory segfaults, core dumps
and memory leaks.
Code that could cause undefined behavior can still be written,
but it is strictly bounded in blocks where the compiler is relaxed.
This relaxation implies that the language is also low-level.
Another key feature to the performance of Rust is zero cost abstraction,
which means that generic types and function abstractions are resolved at compile-time.
Conditional compilation and compile-time computations are also extensively used.
\\
There are also many features concerning the programming experience, such as
advanced metaprogramming and code generation using macros, intelligent compiler,
dependency system (Cargo), modern syntax and many tools to ease development.

\subsection{RabbitMQ}

RabbitMQ is a popoular message broker implementing many messaging protocols.
Message brokers such as RabbitMQ can make an infrastructure to route messages,
validate them and transform them. Messages queue are used
to store messages. Multiple consumers may consume messages from a queue. \\
RabbitMQ servers can also form a cluster. \texttt{todo}

\end{document}